A Comparative study of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-22 latex/paper.tex
Added university name in author section

\author{Mathieu Dugr\'e, Val\'erie Hayot-Sasson, Tristan Glatard\\
Department of Computer Science and Software Engineering\\
Montr\'eal, Qu\'ebec, Canada
}

>>>>

\author{Mathieu Dugr\'e, Val\'erie Hayot-Sasson, Tristan Glatard\\
Department of Computer Science and Software Engineering\\
Concordia University, Montr\'eal, Qu\'ebec, Canada
}
